Ecuador plant trait TRY Cleaning

### 2022-12-02 code/L1/L1_Ecuador_plants_TRY.Rmd
simple rename

# Export preprocessed TRY data
```{r}
# Export the data into a CSV file
ecuador_TRY_plant_traits_path <- file.path(output_path,"Ecuador_TRY_plant_traits.csv")
write.csv(num_traits_georef_wider, file = ecuador_TRY_plant_traits_path)
```

>>>>

# Export TRY data
```{r}
# Export the data into a CSV file
ecuador_TRY_plant_traits_path <- file.path(output_path,"Ecuador_TRY_plant_traits.csv")
write.csv(num_traits_georef_wider, file = ecuador_TRY_plant_traits_path)
```
